Untrusted B2B Collaboration using the Blockchain

### 2018-07-30 paper/paper.tex
Update repo name and keywords

	\keywords{Business Processes \and BPMN \and Choreographies \and Blockchain \and Ethereum \and Smart Contracts}
\end{abstract}
%
\section{Introduction}
% BPM
Business Process Management (BPM) allows organizations to identify, structure and understand the tasks and processes they employ to achieve their business goals.
%Process Models
In BPM, process models are used to document how these goals can be reached, visually describing the participants, activity flow and data objects involved.

@@

The recursive initialization ensures that all contracts that are part of the process instance will be created by one function call.
All other organizations can detect the created instances by watching the factory contract, using a trigger.

@@

In the following, we will formally describe our contract implementations.
The implemented contracts can be found in our repository at \url{https://github.com/p-otto/ProcessesMeetBlockchain2018/tree/master/armadillo/resources}.
% TODO repo & hbox

@@

In the following, we will briefly present the tools we implemented integrate process management with our blockchain approach.
The implementation can be found at \url{https://github.com/p-otto/armadillo}, in the \texttt{armadillo} and \texttt{eth\_admin} folders, respectively.

@@

As a way of joining process execution with our blockchain architecture, we developed a single page web application (see Figure \ref{fig:armadillo}) in JavaScript and HTML, using the Vue.js framework\footnote{\url{https://vuejs.org}}.
With the help of the Web3 Ethereum JavaScript API\footnote{\label{web3}\url{https://github.com/ethereum/web3.js/}}, we can trigger contract functions based on user actions in the applications user interface.
Armadillo also implements the upload and rendering of BPMN diagrams using the bpmn.js toolkit\footnote{\url{https://bpmn.io/toolkit/bpmn-js/}}.
Building upon the BPMN viewer provided in the toolkit, we implemented the handling of user clicks on \emph{BPMN Service Tasks}, which allowed us to use the viewer as a process engine mock.
A screencast of the full choreography can be found in the respository under \url{https://github.com/p-otto/armadillo/blob/master/presentation/armadillo-screencast.mp4}.
% TODO repo, hbox etc.

>>>>

	\keywords{Business Processes \and Choreographies \and Blockchain \and Smart Contracts}
\end{abstract}
%
\section{Introduction}
% BPM
Business Process Management (BPM) allows organizations to identify, structure and understand the tasks and processes they employ to achieve their business goals.
%Process Models
In BPM, process models are used to document how these goals can be reached, visually describing the participants, activity flow and data objects involved.

@@

The recursive initialization ensures that all contracts that are part of the process instance will be created by one function call.
All other organizations can detect the created instances by watching their factory contract, using a trigger.

@@

In the following, we will formally describe our contract implementations.
The specific implemented contracts can be found in our repository in the folder\\\url{https://github.com/p-otto/Armadillo/tree/master/armadillo/resources}.

@@

In the following, we will briefly present the tools we implemented integrate process management with our blockchain approach.
The implementation can be found at \url{https://github.com/p-otto/Armadillo}, in the folders \texttt{armadillo} and \texttt{eth\_admin}, respectively.

@@

As a way of joining process execution with our blockchain architecture, we developed a single page web application (see Figure \ref{fig:armadillo}) in JavaScript and HTML, using the Vue.js framework\footnote{\url{https://vuejs.org}}.
With the help of the Web3 Ethereum JavaScript API\footnote{\label{web3}\url{https://github.com/ethereum/web3.js/}}, we can trigger contract functions based on user actions in the applications user interface.
Armadillo also implements the upload and rendering of BPMN diagrams using the bpmn.js toolkit\footnote{\url{https://bpmn.io/toolkit/bpmn-js/}}.
Building upon the BPMN viewer provided in the toolkit, we implemented the handling of user clicks on \emph{BPMN Service Tasks}, which allowed us to use the viewer as a process engine mock.
A screencast of the full choreography can be found in the respository under \url{https://github.com/p-otto/Armadillo/blob/master/armadillo-screencast.mp4}.
